The Small World Network Effect in Software Project Teams \author{Kevin Peterson\\ \small \texttt{pete1968@umn.edu} }

### 2013-12-06 paper/main.tex
Submitted.

To validate the hypothesis, we expect to find that intermediate values of $Q$ will be correlated with more popular projects. To explore this possibility, we first compare the popularity given $Q$ values as shown in figures \ref{fig:q_fc_graph} and \ref{fig:q_sf_graph}. The $Q$ values do display the inverse U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi\cite{uzzi2005collaboration}.

@@

\noindent\\\textit{\textbf{New contributors are good, as long as the core team remains intact.}}\\
Both participants mentioned the idea of keeping a ``core" team intact, and was an often cited concept in both interviews. This concept appears to align with the idea of a \textit{core/periphery}\cite{borgatti2000models}, where the graph under study contains one (or many) tightly interconnected subgraphs, with less tightly connected nodes radiating out from this core.

>>>>

To validate the hypothesis, we expect to find that intermediate values of $Q$ will be correlated with more popular projects. To explore this possibility, we compare the popularity given $Q$ values as shown in figures \ref{fig:q_fc_graph} and \ref{fig:q_sf_graph}. The $Q$ values do display the inverse U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi\cite{uzzi2005collaboration}, and supports our hypothesis.

@@

\noindent\\\textit{\textbf{New contributors are good, as long as the core team remains intact.}}\\
Both participants mentioned the idea of keeping a ``core" team intact, and it was an often cited concept in both interviews. This concept appears to align with the idea of a \textit{core/periphery}\cite{borgatti2000models}, where the graph under study contains one (or many) tightly interconnected subgraphs, with less tightly connected nodes radiating out from this core.
